---
title: "R Notebook"
output: html_notebook
---

# Introduction
The purpose of this notebook is to simplify finding which of my wines are stored in a specified location without regard to any other locations where the wines in the specified location may be stored. We are only concerned with my cellar and the production database. The functions are not designed to work with other cellars (of which there really are none!). 

# Fetch My Cellar
Note the manipulation of the global.R variable test.run.

```{r}
test.run <- F
my.cellar <- db.fetch.cm("drwo@woteki.com", "Wine!Warrior") %>%
    db.fetch.cellar()
# test.run <- T
```

```{r}
(my.cellar <- my.cellar %>%
   select(ID, Vint, Producer, Wine, Location, Num))
```

# Check Total Number of Bottles
Total count:
```{r}
num.total <- function(cellar = my.cellar) {
  sum(cellar$Num)
}
num.total()
```

# Find all wines in a specified location
Given a location, find all the wines that are in that location. The data that are returned include all the other locations those wines are stored and the total number of bottles of each wine.
```{r}
find.for.location <- function(location, cellar = my.cellar) {
  
  # local utility function
  # Given a wine in the cellar, represented by a row of my.cellar, and a location in the cellar, determine whether there is any of that wine in the specified location:
  location.has.wine <- function(wine, location) {
    locs <- str_extract_all(wine$Location, "[[:alpha:]]+")
    # print(locs)
    location %in% locs[[1]]
  }
  
  wines <- tibble(ID = 0, vint = 0, producer = "", wine = "", location = "", total.num = 0)
  for (i in 1:nrow(cellar)) {
    wine <- cellar[i, ]
    if (location.has.wine(wine, location) ) {
      l <- wine$Location
      n <- wine$Num
      wine <- tibble(ID = wine$ID, vint = wine$Vint, producer = wine$Producer, wine = wine$Wine, location = l, total.num = n)
      wines <- wines %>%
        bind_rows(wine)
    }
  }
  wines %>% filter(location != "")
}
```

# Tabulate Location
Unlike the previous function, this function returns only the number of each wine that are in the specified location without regard to any other locations where the wines in the specified location may be stored. This function fulfills the goal stated in the introduction to the notebook. It makes it easier to see which wines are in the specified location without regard to other places the wins may be stored.

```{r}
tab.for.location <- function(location, cellar = my.cellar) {
  
  # a given wine may be stored in several locations
  # this function finds how many bottles of it are in the specified location and discards the rest of the locations
  isolate.location <- function(a.wine) {
    # parse the location information
    locs <- str_extract_all(a.wine$location, "[[:alpha:]]+")[[1]]
    # parse the number of bottles info
    nums <- str_extract_all(a.wine$location, "\\d+")[[1]]
    # if length(nums) == 0 it's because there is only one location and all of the wine is in that location
    if (length(nums) == 0) nums <- as.character(a.wine$total.num)
    # locs and nums should now be 2 vectors of equal length where locs is all of the locations where the wine is stored
    # and nums is the corresponding number of bottles
    # create a tibble and from these vectors, filter to the desired location and return the result
    tibble(loc = locs, num = nums) %>%
      filter(loc == location)
  }
  
  # set up a header for a tibble that will hold all the wines that are in the sepcified location
  wines <- tibble(ID = 0, vint = 0, producer = "", wine = "", location = "", num = 0)
  # find all the wines that have at least some bottles specified by the input parameter location
  found.wines <- find.for.location(location, cellar)
  for (i in 1:nrow(found.wines)) {
    w <- found.wines[i, ]
    il <- isolate.location(w)
    w <- tibble(ID = w$ID, vint = w$vint, producer = w$producer, wine = w$wine, location = il$loc, num = as.numeric(il$num))
    wines <- wines %>%
      bind_rows(w)
  }
  # get rid of the summy top row of wines and return the result
  wines %>% filter(location != "") 
}
```

